%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Allixo}{Sep 2018 -- Present}
    {Engineer}{Mount Vernon, Washington}
    \resumeItemListStart
      \resumeItem{Support moving on-prem workloads to Azure Cloud.}
      \resumeItem{Azure automations to encapsulate all aspects of running a business
      in the cloud including billing and scale.}
      \resumeItem{Automating software toolstack deployments via RMM or Intune.}
      \resumeItem{Backend management of linux servers and Azure Kubernetes.}
      \resumeItem{Support LOB migrations and automations (C++,C\#,Python,SQL).}
      \resumeItem{Regular planning for service improvement and ensuring industry standards.}
      \resumeItem{Open-source development for multiple tools and scripts.}
    \resumeItemListEnd

  \resumeSubheading
    {HazardBrick LLC}{Nov 2012 -- Present}
    {Owner}{Mount Vernon, Washington}
    \resumeItemListStart
      \resumeItem{Managing software development company as owner.}
      \resumeItem{Development of LOB applications.}
      \resumeItem{Development of custom websites and content management.}
      \resumeItem{Implimentation of out-of-box solutions.}
    \resumeItemListEnd


  \resumeSubheading
    {First Transit}{Aug 2015 -- Aug 2018}
    {Apprentice Mechanic}{Everett, Washington}
    \resumeItemListStart
      \resumeItem{Work with team of mechanics and management for service delivery.}
      \resumeItem{Advanced troubleshooting of diesel engines, electrical, and air systems.}
      \resumeItem{Keep up safety standards based on industry best practice.}
      \resumeItem{Training on advanced bus systems and safety protocols.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
